Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics

### 2023-07-25 03_marlin_paper.qmd
updating a few things to reflect some changes to marlin

patch_biomass <-
  map_df(coral_sim, ~ map_df(.x, ~tibble(biomass = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step") %>%
  mutate(step = as.numeric(step)) %>%
  left_join(grid, by = "patch")

@@

critter_biomass <-
  map_df(blue_sim, ~ map_df(.x, ~tibble(ssb = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step") %>%
  mutate(step = as.numeric(step)) %>%
  left_join(grid, by = "patch") %>% 
  group_by(critter, step) %>% 
  summarise(ssb = sum(ssb)) %>% 
  group_by(critter) %>% 
  mutate(depletion = ssb / ssb[step == 0])

@@

patch_biomass <-
  map_df(blue_climate_sim, ~ map_df(.x, ~tibble(biomass = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step") %>%
  mutate(step = as.numeric(step)) %>%
  left_join(grid, by = "patch")

@@

coral_frontier <- tmp %>% 
  ggplot(aes(delta_biodiv, delta_yield)) + 
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_line(alpha = 0.8, aes(color = placement_strategy),size = 1.1) + 
  geom_text_repel(data = frontier_labels, aes(label = pmpa, color = placement_strategy), min.segment.length = 0, box.padding = 0.2, show.legend = FALSE) +
  scale_x_continuous(name = "Change in Total SSB/SSB0", labels = scales::label_percent(accuracy = 1), guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(name = "Change in Yield", labels = scales::label_percent(accuracy = 1)) + 
  scale_color_manual(values = c("tomato", "steelblue"),name = '') +
  guides(fill = guide_legend(order = 1, override.aes = list(size = 4))) + 
  labs(tag = "C")  + 
  theme(
    legend.position = c(0.7, .85),
    legend.background = element_rect(fill = "transparent"),
    legend.text = element_text(size = 8)
  )

>>>>

patch_biomass <-
  map_df(coral_sim, ~ map_df(.x, ~tibble(biomass = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step") %>%
  mutate(step = marlin::clean_steps(step)) %>%
  left_join(grid, by = "patch")

@@

critter_biomass <-
  map_df(blue_sim, ~ map_df(.x, ~tibble(ssb = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step") %>%
  mutate(step = marlin::clean_steps(step)) %>%
  left_join(grid, by = "patch") %>% 
  group_by(critter, step) %>% 
  summarise(ssb = sum(ssb)) %>% 
  group_by(critter) %>% 
  mutate(depletion = ssb / ssb[step == 0])

@@

patch_biomass <-
  map_df(blue_climate_sim, ~ map_df(.x, ~tibble(biomass = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step") %>%
  mutate(step = marlin::clean_steps(step)) %>%
  left_join(grid, by = "patch")

@@

coral_frontier <- tmp %>% 
  ggplot(aes(delta_biodiv, delta_yield)) + 
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_line(alpha = 0.8, aes(color = placement_strategy),size = 1.1) + 
  geom_text_repel(data = frontier_labels, aes(label = pmpa, color = placement_strategy), min.segment.length = 0, box.padding = 0, show.legend = FALSE, nudge_x = .25, size = 5) +
  scale_x_continuous(name = "Change in Total SSB/SSB0", labels = scales::label_percent(accuracy = 1), guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(name = "Change in Yield", labels = scales::label_percent(accuracy = 1)) + 
  scale_color_manual(values = c("tomato", "steelblue"),name = '') +
  guides(fill = guide_legend(order = 1, override.aes = list(size = 4))) + 
  labs(tag = "C")  + 
  theme(
    legend.position = c(0.7, .85),
    legend.background = element_rect(fill = "transparent"),
    legend.text = element_text(size = 8)
  )
